How to write cross-interpreter programs

### 2010-02-17 talk/pycon2010/crossinterp/talk.tex
Progress

\begin{frame}[fragile]
  \frametitle{Exceptions}
  \begin{itemize}
    \item TypeError vs AttributeError change often between implementations,
      even CPython versions
    \item don't rely on exception string messages (they may differ)
    \item also means - don't use doctests
  \end{itemize}
  \begin{verbatim}
try:
  ...
except ImportError, ie:
  if str(ie) != '...':
    raise
  \end{verbatim}
\end{frame}

\begin{frame}[fragile]
  \frametitle{Subclasses of builtin types and overriding}
  \begin{itemize}
    \item in general overridden methods on subclassed builtin types are not 
      invoked by preexisting other methods
      \begin{verbatim}
class d(dict):
  def __getitem__(self, e):
    ...
      \end{verbatim}
    \item would {\ttfamily keys()} go via this getitem?
    \item there can be corner cases, for example when
      there are more than one object involved
    \item tests are your friend
  \end{itemize}
\end{frame}

@@

\begin{frame}
  \frametitle{Don't rely on refcounting}
  \begin{itemize}
    \item example {\ttfamily open('x', 'w').write('stuff')}
    \item on refcounting, flushes file immediately
    \item on any other GC, it might be deferred for
      a while
    \item the single most-common problem when fixing twisted
  \end{itemize}
\end{frame}

\begin{frame}
  \frametitle{\_\_del\_\_}
  \begin{itemize}
    \item in case of resurrection CPython will call {\ttfamily \_\_del\_\_} multiple times,
      other Pythons exactly once
    \item cycles with \_\_del\_\_s are not collected by CPython,
      PyPy breaks them randomly instead
    \item in PyPy (xxx Jython?) \_\_del\_\_ cannot be attached to classes after creation
  \end{itemize}
\end{frame}

@@

>>>>

\begin{frame}[fragile]
  \frametitle{Exceptions}
  \begin{itemize}
    \item TypeError vs AttributeError change often between implementations,
      even CPython versions
    \item don't rely on exception string messages (they may differ)
  \end{itemize}
  \begin{verbatim}
try:
  ...
except ImportError, ie:
  if str(ie) != '...':
    raise
  \end{verbatim}
  \pause
  \begin{itemize}
    \item also means - don't use doctests
  \end{itemize}
\end{frame}

\begin{frame}[fragile]
  \frametitle{Subclasses of builtin types}
  \begin{itemize}
    \item in general overridden methods on subclassed builtin types are not 
      invoked by preexisting other methods
      \begin{verbatim}
class d(dict):
  def __getitem__(self, e):
    ...
      \end{verbatim}
    \item would {\ttfamily keys()} go via this getitem?
    \item tests are your friend
  \end{itemize}
\end{frame}

@@

\begin{frame}[fragile]
  \frametitle{Don't rely on refcounting}
  \begin{itemize}
    \item example
      \begin{verbatim}
open('x', 'w').write('stuff')
      \end{verbatim}
    \item on refcounting, flushes file immediately
    \item on any other GC, it might be deferred for
      a while
    \item the single most-common problem when fixing twisted
  \end{itemize}
\end{frame}

\begin{frame}
  \frametitle{\_\_del\_\_}
  \begin{itemize}
    \item resurrection on CPython will call {\ttfamily \_\_del\_\_} multiple times,
      other Pythons exactly once
    \item cycles with \_\_del\_\_s are not collected by CPython,
      PyPy breaks them randomly instead
    \item in PyPy and Jython \_\_del\_\_ cannot be attached to classes after creation
  \end{itemize}
\end{frame}

@@

\begin{frame}
  \frametitle{Questions?}
  \begin{itemize}
    \item http://morepypy.blogspot.com
    \item http://pypy.org
  \end{itemize}
\end{frame}
